\documentclass{article}

\usepackage{amssymb}

\author{Wesley Gould, John Clark, and Elizabeth McNany}
\date{17 December 2011}
\title{EECS 341 Final Report Difficult Queries}

\begin {document}
\maketitle

\section{Queries We Used}

The various types of queries used in our project are listed below in plain English.  Most of them are fairly simple due to our heavy use of keys, but a couple are slightly more complicated.

We had queries to: \newline
Add, edit, or delete a Contact.  \newline
Get a list of contacts (optionally matching a pid) and also their information from the member table (if they are also a member). \newline
Convert from caseid to pid. \newline
Check if a person is a contact. \newline
Add, edit, or delete a Member. \newline
Check if a person is a member.  \newline
Get a list of member (optionally matching a pid) and also their information from the contact table (if they are also a contact). \newline
Add, edit, or delete a Officer.  \newline
Get a listing of the full officer history, including all fields from the contacts, officer\_history and officer\_positions tables. \newline
Add, edit, or delete a Officer Position. \newline
Check if a person was an officer. \newline
Add, edit, or delete a Stabilizer. \newline
Add, edit, or delete a Arrow. \newline
Add, edit, or delete a Equipment. \newline
Add, edit, or delete a Riser. \newline
Add, edit, or delete a Limb. \newline
Add, edit, or delete a Loan. \newline
View all equipment. \newline
See if a piece of equipment is checked out. \newline
Check in a piece of equipment. \newline
Add an entry to the tracelog. \newline
View the tracelog by user, by action or the whole tracelog. \newline
See if a file exists. \newline
Find a file's fid given the name, description or owners. \newline
List and edit the file permissions of a file. \newline
Add, edit, or delete a Score. \newline

\section{5 Hardest Queries}

Again due to our heavy use of keys, there aren't many difficult queries, and most of the hard ones are just joins on a key.  Below are what we think to be the most difficult.

Our five hardest queries were:\newline

\begin{enumerate}
\item Get a list of contacts (optionally matching a pid) and also their information from the member table (if they are also a member). 
\item Convert from caseid to pid. 
\item Get a list of member (optionally matching a pid) and also their information from the contact table (if they are also a contact). 
\item Get a listing of the officerhistory, including all fields from the contacts, officer\_history and officer\_positions tables between a start date and end date. 
\item Get a listing of the full officer history, including all fields from the contacts, officer\_history and officer\_positions. 
\end{enumerate}
\subsection{SQL}

\begin{enumerate}

\item SELECT * FROM contact LEFT JOIN member ON contact.pid=member.pid WHERE pid=contact.pid
\item SELECT pid FROM member WHERE netid=caseid
\item SELECT * FROM member LEFT JOIN contact ON member.pid = contact.pid WHERE member.pid=pid
\item SELECT * FROM officer\_history H, officer\_positions P, contact C WHERE H.pos\_id = P.pos\_id AND H.pid = C.pid
\item SELECT * FROM officer\_history H, officer\_positions P, contact C WHERE H.pos\_id = P.pos\_id AND H.pid = C.pid AND CURDATE() BETWEEN start\_date AND end\_date

\end{enumerate}

\subsection{RA}
Note that the $\ltimes$ symbol is supposed to represent a left outer join, but we had a hard tim finding the correct latex symbol.

\begin{enumerate}
\item $\left(\sigma_{pid=contact.pid} contact \right) \ltimes_{contact.pid=member.pid} member$  
\item $\pi_{member.pid}\left(\sigma_{member.netid=caseid} member\right)$
\item $\left(\sigma_{pid=member.pid} member \right) \ltimes_{contact.pid=member.pid} contact$
\item $ \left(officer\_history \bowtie_{officer\_history.pos\_id=officer.pos\_id} officer\_positions\right) \bowtie_{pid=contact.pid} contact$
\item $ \left(\left(\sigma_{end\_date>=CURDATE()>=start\_date}officer\_history\right) \bowtie_{pos\_id=officer.pos\_id} officer\_positions\right) $ $\bowtie_{pid=contact.pid} contact$
\end{enumerate}

\subsection{RC}

For this section, officer\_history will be denoted by O, officer\_positions by P, contact by C, and member by M.

\begin{enumerate}
\item $\{t^{(22)}|(\exists(c)(C(c)\wedge c.pid=pid \wedge $ $t[1]=c.pid\wedge $ $t[2]=c.first\_name\wedge$ $t[3]=c.last\_name\wedge$ $t[4]=c.address\wedge$ $t[5]=c.city\wedge$ $t[6]=c.state\wedge$ $t[7]=c.zipcode\wedge$ $t[8]=c.email\wedge$ $t[9]=c.phone\wedge\exists(m)(M(m)\wedge m.pid=c.pid\wedge$ $t[10]=m.mid\wedge$ $t[11]=m.netid\wedge$ $t[12]=m.studentid\wedge$ $t[13]=m.bow\_preference\wedge$ $t[14]=m.handedness\wedge$ $t[15]=m.membership\_expiration\wedge$ $t[16]=m.usca\_id\wedge$ $t[17]=m.usca\_expiration\wedge$ $t[18]=m.emergency\_name\wedge$ $t[19]=m.emergency\_phone\wedge$ $t[20]=m.insurance\_company\wedge$ $t[21]=m.policy\_number)))\}$
\item $\{t^1|\exists(m) M(m)\wedge t[1]=m.pid\wedge m.netid=caseid\}$
\item $\{t^{(22)}|(\exists(m)(M(m)\wedge m.pid=c.pid\wedge$ $t[1]=m.mid\wedge$ $t[2]=m.netid\wedge$ $t[3]=m.studentid\wedge$ $t[4]=m.bow\_preference\wedge$ $t[5]=m.handedness\wedge$ $t[6]=m.membership\_expiration\wedge$ $t[7]=m.usca\_id\wedge$ $t[8]=m.usca\_expiration\wedge$ $t[9]=m.emergency\_name\wedge$ $t[10]=m.emergency\_phone\wedge$ $t[11]=m.insurance\_company\wedge$ $t[12]=m.policy\_number\wedge \exists(c)(C(c)\wedge c.pid=pid \wedge $ $t[13]=c.pid\wedge $ $t[14]=c.first\_name\wedge$ $t[15]=c.last\_name\wedge$ $t[16]=c.address\wedge$ $t[17]=c.city\wedge$ $t[18]=c.state\wedge$ $t[19]=c.zipcode\wedge$ $t[20]=c.email\wedge$ $t[21]=c.phone)))\}$

\item  $\{t^{(14)}|\exists(o)(O(o)\wedge t[1]=o.pid \wedge$ $t[2]=o.pos\_id \wedge$ $t[3]=o.start\_date \wedge$ $t[4]=o.end\_date \wedge \exists(p)(P(p)\wedge p.pos\_id=o.pod\_id  \wedge$ $t[5]=p.title \wedge$ $t[6]=p.description \wedge \exists(c)(C(c)\wedge p.pid=c.pid \wedge$ $t[7]=c.first\_name \wedge$ $t[8]=c.last\_name\wedge$ $t[9]=c.address\wedge$ $t[10]=c.city \wedge$ $t[11]=c.state\wedge$ $t[12]=c.zipcode\wedge$ $t[13]=c.email\wedge$ $t[14]=c.phone )))\}$

\item \item  $\{t^{(14)}|\exists(o)(O(o)\wedge t[1]=o.pid \wedge$ $t[2]=o.pos\_id \wedge$ $t[3]=o.start\_date \wedge$ $t[4]=o.end\_date \wedge \exists(p)(P(p)\wedge p.pos\_id=o.pod\_id  \wedge$ $t[5]=p.title \wedge$ $t[6]=p.description \wedge \exists(c)(C(c)\wedge p.pid=c.pid \wedge$ $t[7]=c.first\_name \wedge$ $t[8]=c.last\_name\wedge$ $t[9]=c.address\wedge$ $t[10]=c.city \wedge$ $t[11]=c.state\wedge$ $t[12]=c.zipcode\wedge$ $t[13]=c.email\wedge$ $t[14]=c.phone ))\wedge o.start\_date<=CURDATE()<=o.end\_date  )\}$


\end{enumerate}

\end{document}
